### 2014-10-01 tex/definitions.tex
Rewrote theorem 1
Added definition commentary

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as
\end{definition}

@@

@@

The total number of references in a summary state and a lazy state that it represents are generally not the same. However, the number of references on the stack in either state is always the same. In order to make the distinction between different types of references, we partition the set of natural numbers using modular arithmetic.

@@

@@

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relat
es machine states with successor states. Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$. Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

\begin{definition}
A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
\end{definition}

\begin{definition}
A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
A lazy state is also a summary state by definition.
\end{definition}

\begin{definition}
A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}{r}\ (\\
\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
\end{array}
\]
\end{definition}
%\begin{definition}
%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$. A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
%\end{definition}
%
%%For 
%\begin{comment}
%\begin{definition}
%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
%\end{definition}
%\end{comment}

@@

@@

\begin{definition}
\label{def:interstate}
\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules. For example, the transition $s_x \rightarrow_\phi s_y$ may be equivalent to a sequence of simpler transitions $s_x \rightarrow_\alpha s_a \rightarrow_\beta s_b \rightarrow_\gamma s_y$.  When reasoning about this equivalent transition sequence, it can be useful to discuss the notional intermediate states $s_a$ and $s_b$. However, it is important to remember that $s_a$ and $s_b$ are not technically involved in the transition $s_x \rightarrow_\phi s_y$, and indeed may not be part of any feasible state sequence under transition relation $\rightarrow_\phi$.
\end{definition}

@@

@@

@@

>>>>

In Javalite, states are strings that match a certain pattern.

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

@@

You can think references as a pointers to sets of locations. More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to. Within a machine state, references are string encodings of integers.

@@

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

@@

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

@@

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$. Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

%\begin{definition}
%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
%\end{definition}
%
%\begin{definition}
%A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
%$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
%A lazy state is also a summary state by definition.
%\end{definition}

\begin{definition}
A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}(r)\ (\\
\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
\end{array}
\]
\end{definition}

%\begin{definition}
%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$. A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
%\end{definition}
%
%%For 
%\begin{comment}
%\begin{definition}
%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
%\end{definition}
%\end{comment}

@@

At times, it is useful to classify states in terms of patterns that the state strings match. In concrete terms, this is similar to asking what will be the next instruction to execute. For example, we know that left-hand states matching the pattern $ \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ only appear in the Field Access rule.

@@

%\begin{definition}
%\label{def:interstate}
%\textbf{Intermediate states} are imaginary placeholder states used when reasoning about complex transition rules in terms of simpler sub-rules. For example, the transition $s_x \rightarrow_\phi s_y$ may be equivalent to a sequence of simpler transitions $s_x \rightarrow_\alpha s_a \rightarrow_\beta s_b \rightarrow_\gamma s_y$.  When reasoning about this equivalent transition sequence, it can be useful to discuss the notional intermediate states $s_a$ and $s_b$. However, it is important to remember that $s_a$ and $s_b$ are not technically involved in the transition $s_x \rightarrow_\phi s_y$, and indeed may not be part of any feasible state sequence under transition relation $\rightarrow_\phi$.
%\end{definition}

@@

We will later be concerned with establishing whether one state represents another state. We want to say that one state represents another state if equivalent paths lead out from each state. This path-centric notion of equivalence is known as functional equivalence. In establishing functional equivalence between states, it is important to determine whether the heaps within the states are themselves functionally equivalent. Two heaps are functionally equivalent if the same sequence of field accesses in each heap produces equivalent results. We define heap functional equivalence using a co-inductive definition of homomorphism over the access paths in the heaps.

@@

Since the access paths in any given heap are bound by certain constraints, to preserve control flow equivalence we must establish whether the collection of any constraints in a given heap are collectively feasible. The homomorphism constraint is the conjunction of all constraints in the image of the represented heap in the representer heap.

@@

The representation relation combines the previously established notions of heap homomorphism and feasibility with the added constraint that the variables, expressions, and continuation strings must match between the pairs of states.
